---
title: "Excel Challenges"
author: "Anil Goyal"
date: "2024-04-10"
output: html_document
---
```{r}
library(tidyverse)
library(readxl)
library(janitor)
```

## Excel Challenge 446
```{r}
library(igraph)

adj_df <- read_xlsx("Excel/Excel_Challenge_446 - Top 3 Min Distance.xlsx", range = cell_cols(LETTERS[1:8]))
adj_df %>% 
  column_to_rownames("Cities") %>% 
  as.matrix() %>% 
  graph_from_adjacency_matrix(weighted = "Distance") %>% 
  igraph::as_data_frame() %>% 
  mutate(from_city = pmin(from, to),
         to_city = pmax(from, to), .before = Distance) %>% 
  select(-from, -to) %>% 
  distinct() %>% 
  slice_min(n = 3, order_by = Distance) %>% 
  mutate(Rank = dense_rank(Distance), .before = 1) %>% 
  rename_with(.fn = ~janitor::make_clean_names(.x, case = "title"))
```


## Excel Challenge 445 (444 - 30th April 2024)
```{r}
c(
  list(0),
  rep(list(c(-0.5, 0.5)), 5),
  rep(list(-2:2), 3),
  rep(list(-3:3), 3),
  rep(list(-4:4), 3),
  list(c(-6:-3, 3:6)),
  list(c(-8:-5, 5:8)),
  list(-10:10),
  list(c(-11:-6, 6:11)),
  list(c(-15:-8, 8:15))
) %>%
  map_dfr( ~ setNames(.x, paste0("V_", seq_along(.x)))) %>%
  mutate(col = row_number()) %>%
  pivot_longer(
    -col,
    names_sep = "_",
    names_to = c(".value", "row"),
    names_transform = list(row = as.integer)
  ) %>%
  na.omit() %>%
  mutate(
    shape = case_match(col,
                       1 ~ "A",
                       3 ~ "B",
                       2 ~ "C",
                       .default = "D"),
    shape = ifelse(row == 2 & col == 2, "E", shape)
  ) %>%
  ggplot(aes(V, col, shape = shape)) +
  geom_point(size = 4) +
  scale_y_reverse() +
  scale_shape_manual(values = c(A = 73, B = 48, C = 47, D = 4, E = 92)) +
  theme_void() +
  theme(legend.position = "none")
```




## Excel Challenge 444
```{r}
# Creating given problem
data.frame(
  Numbers = c(1, 8, 41)
) %>% 
  # Creating New column for desired Sequence
  mutate(`Answer Expected` = map_chr(Numbers, .f = \(.a) {
    # Using purrr::accumulate
    accumulate(1:4, ~ .x %>% 
                 # split all digits into single digits
                 str_split("") %>% 
                 # unlist the above output
                 unlist() %>% 
                 # generate a frequency table
                 # as well as sort it on the basis of
                 # digits available in given number
                 {table(.)[unique(.)]} %>% 
                 # this will create a data frame of above table
                 tibble::enframe() %>% 
                 # interleave both columns
                 {c(rbind(.$value, .$name))} %>% 
                 # Paste the string back together
                 str_c(collapse = ""),
               # Take initial value for purrr::accumalate as the given number
               .init = .a
               # Remove first result from the output
               # which will be same as given first number
               )[-1] %>% 
      # Unlist the sequence digits (from the output list)
      unlist() %>% 
      # Collapse them back
      str_c(collapse = ", ")
  }))
```



## Excel Challenge 443
```{r}
mat <- read_xlsx("Excel/Excel_Challenge_443 - Birds Search.xlsx",
                 range = "B2:K11",
                 col_names = FALSE) %>%
  as.matrix()

birds <- read_xlsx("Excel/Excel_Challenge_443 - Birds Search.xlsx", 
                   range = cell_cols("M"))

paste0(t(mat), collapse = "") %>% 
  str_replace_all(
    birds %>% 
      mutate(rep_c = map_chr(Birds, ~str_c(rep("X", nchar(.x)), collapse = ""))) %>% 
      tibble::deframe()
  ) %>% 
  str_split("") %>% 
  unlist() %>% 
  matrix(nrow=nrow(mat), byrow = TRUE) %>% 
  # alternative
  # {`[<-`(mat, mat == ., "x")}
  {replace(mat, mat == ., "x")} 

```



## Excel Challenge 442
```{r}
cipher <- function(key, MSG){
  key_rank <- key %>% 
    str_split("") %>% 
    unlist() %>% 
    order()
  
  msg <- MSG %>% 
    str_replace_all(" ", "") %>% 
    str_split("") %>% 
    unlist()
  
  if(length(msg) %% length(key_rank) != 0){
    msg <- c(msg, rep(NA, length(key_rank) - (length(msg) %% length(key_rank))))
  }
  
  matrix(msg, ncol = length(key_rank), byrow = TRUE)[, key_rank] %>% 
    apply(2, function(.x) str_c(.x[!is.na(.x)], collapse = "")) %>% 
    str_c(collapse = " ")
}

cipher("swan", "battle won")
cipher("bee", "spy on prowl")
cipher("xono", "carry firearms")
cipher("great", "microsoft excel")
```

## Excel Challenge 441
```{r}
df <- data.frame(
  stringsAsFactors = FALSE,
                 Problem = c("3-7","5, 3-8",
                             "12, 15-18, 24","5-6, 8-10, 12","2, 8-10, 9-13, 12",
                             "999-1001, 1000, 1002-1004")
      )

df %>% 
  mutate(Answer = Problem) %>% 
  separate_rows(Answer, sep = ", ") %>% 
  reframe(Answer = unlist(map(Answer, ~{
    if(str_detect(.x, "-")){
      unlist(str_split(.x, "-")) %>% 
        as.integer() %>% 
        {.[1]:.[2]}
     } else {
      as.integer(.x)
    }
  })), .by = Problem) %>% 
  distinct() %>% 
  summarise(Answer = str_c(sort(Answer), collapse = ", "), .by = Problem)
```



## Excel Challenge 440
List the numbers between 1 to 100 which can be expressed as sum of two perfect squares of natural numbers (natural numbers don't include `0`).
Ex. `5` which can be expressed as `1^2 + 2^2`.
```{r}
(1:10)^2 |>   
  combn(2) |>   
  colSums() |>   
  unique() |>
  sort() |>   
  {\(.x) .x[.x <= 100]}()
```


## Excel Challenge 435: Draw a boat
Using `ggplot2` here just for fun.
```{r}
map(c(0:7, 11:8),
    ~ 12 + seq(-1 * (.x ), .x, by = 1)) %>% 
  imap_dfr(~ .x %>% 
        as_tibble() %>% 
        set_names("col") %>% 
        mutate(row = .y)) %>% 
  mutate(shape = case_when(
    row %in% 1:7 ~ "A",
    row == 8 ~ "B",
    TRUE ~ "C"
  )) %>% 
  ggplot(aes(col, row)) +
  geom_point(aes(shape = shape)) +
  scale_y_reverse() +
  scale_shape_manual(values = c(3, 61, 4)) +
  theme_void() +
  theme(legend.position = "none")
```


## Excel Challenge 434: Generating Excel column names matrix
```{r}
n <- 100

{cumsum(seq(n)) - seq(n) + 1} |> 
  cellranger::num_to_letter() |>
  matrix(nrow=20)
```


## Excel Challenge 433: parsing the file/data
```{r}
df <- read_excel("Excel/Excel_Challenge_433 - Text Split.xlsx", range = cell_cols(LETTERS[1]))

df %>% 
  separate(Text, into = c("Levels", "Names"), sep = " : ") %>% 
  separate(Levels, into = paste0("Level", 1:3), sep = "\\.", fill = "right") %>% 
  separate(Names, into = c("First Name", "Last Name"), sep = " ", fill = "right")
```


## Excel Challenge 432: BIFID CIPHER

```{r}
bifid <- function(WORD){
  str_split(WORD, "")  %>% 
    unlist() %>% 
    map(~ which(matrix(LETTERS[-10], nrow = 5, byrow = TRUE) == .x, arr.ind = TRUE) %>% as.vector()) %>% 
    unlist() %>% 
    matrix(ncol = 2, byrow = TRUE) %>% 
    as.vector() %>% 
    split.default(., ((seq_along(.) - 1) %/% 2) + 1 ) %>% 
    map_chr(~matrix(LETTERS[-10], nrow = 5, byrow = TRUE)[.x[1], .x[2]]) %>% 
    str_c(collapse = "")
}

map_chr(c("BATTLE", "FLEX"), bifid)
```


## Excel Challenge 431 (Date: 10 April 2024)

```{r}
library(readxl)
library(tidyverse)

df <- read_excel("Excel/Excel_Challenge_431 - Top 3 Rankings.xlsx", range = cell_cols(LETTERS[1:8]))

df %>%
  mutate(across(-Region, ~ dense_rank(-1 * as.numeric(.x)))) %>% 
  pivot_longer(-Region, names_to = "Year", values_to = "Rank") %>% 
  filter(Rank %in% 1:3) %>% 
  summarise(rank_counts = n(),
            .by = c(Region, Rank)) %>% 
  group_by(Rank) %>% 
  slice_max(rank_counts, n = 1) %>% 
  summarise(Regions = str_c(Region, collapse = ", "))
```

## Excel Challenge 430: Flashlight

```{r}
map_dfr(1:26,
    ~ seq(from = 2*.x -1, length.out = 27 - .x) %>% 
      as_tibble() %>% 
      set_names("x") %>% 
      mutate(char = LETTERS[seq(27 - .x)],
             y = 27 - .x)) %>% 
  ggplot(aes(x, y, label = char)) +
  geom_text() +
  scale_x_reverse() +
  theme_void()
```

